Can Auxiliary Indicators Improve COVID-19 Forecasting and Hotspot Prediction?

### 2021-06-18 forecast/paper/paper.tex

% Please add a significance statement to explain the relevance of your work
\significancestatement{
  TODO % For reference, below is the indicators paper one.

  % To study the COVID-19 pandemic, its effects on society,
  % and measures for reducing its spread, researchers need detailed data on the
  % course of the pandemic. Standard public health data streams suffer
  % inconsistent reporting and frequent, unexpected revisions. They also miss
  % other aspects of a population's behavior, worthy of consideration. We
  % present an open database of COVID signals in the United States, measured at
  % the county level and updated daily. These include traditionally reported
  % COVID cases and deaths, and many others: signals based on measures of
  % mobility, social distancing, internet search trends, self-reported symptoms,
  % and patterns COVID-related activity in de-identified medical insurance 
  % claims. The database provides all signals in a common, easy-to-use format,
  % empowering both  public health research and operational decision-making. 
}

>>>>

% Please add a significance statement to explain the relevance of your work
\significancestatement{Forecasting is a key component in the public health
  response to any fast-moving epidemic or pandemic.  Forecasting the future
  spread some disease process, based on disease activity in the recent
  past---say, using what is known as autoregressive modeling in the time series
  literature---is a basic and widely-used method, which can be especially 
  effective in noisy data settings.  In this paper we ask whether including
  auxiliary indicators as additional features in such an autoregressive model
  can be useful in COVID-19 case forecasting and hotspot prediction.  We find 
  that auxiliary indicators based on de-identified medical insurance claims,
  self-reported symptoms through online surveys, and COVID-related Internet
  search activity all provide a nontrivial boost in accuracy, though their
  utility generally depends the phase of the pandemic that we are in at
  prediction time (upswing, downswing, or flat period).
}

  % TODO % For reference, below is the indicators paper one.
  % To study the COVID-19 pandemic, its effects on society,
  % and measures for reducing its spread, researchers need detailed data on the
  % course of the pandemic. Standard public health data streams suffer
  % inconsistent reporting and frequent, unexpected revisions. They also miss
  % other aspects of a population's behavior, worthy of consideration. We
  % present an open database of COVID signals in the United States, measured at
  % the county level and updated daily. These include traditionally reported
  % COVID cases and deaths, and many others: signals based on measures of
  % mobility, social distancing, internet search trends, self-reported symptoms,
  % and patterns COVID-related activity in de-identified medical insurance 
  % claims. The database provides all signals in a common, easy-to-use format,
  % empowering both  public health research and operational decision-making. 
%}
